Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-05-15 cthpc-2017/paper.tex
Change budget form NTD to USD and correct the spelling

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{placeins}
%\usepackage{flafter}

\usepackage{url}
\usepackage{listings}
% \usepackage{sectsty}
% \usepackage{authblk}
% \graphicspath{{../pdf/}{../jpeg/}}
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

@@

\begin{table}
	\centering
	\caption{Bill Of Materials}
	\label{hardware_list}
	\begin{tabular}{ll}
		Hardware                & Budgets  \\
		Raspberry Pi3 Model B   & 39.79 USD \\
		Raspberry Pi camera     & 23.15 USD  \\
		2S LiPo battery 1300mAh & 7.96 USD  \\
		Sandisk 16G microSD     & 6.13 USD  \\
		L298N motor driver      & 8.72 USD  \\
		Car frame               & 12.44 USD  \\
		DC voltage regulator    &  3.48 USD  \\
		Total                   & 101.67 USD
	\end{tabular}
\end{table}

@@

We refer to MIT Duckietown's experience \cite{Duckietown} and created an artificial environment that the lane detector can be implemented easier. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.

@@

The intrinsic matrix is also refer to the camera projection, it is an ideal linear model consists of focal length, pixel size and principal point, the non-linear effects like lens distortion[\ref{fig:intrinsic}] are usually solved numerically.

@@

Figure \ref{fig:extrinsic} show the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.

@@

\subsubsection{Lane detector work conditions}
$ $
\begin{table}[!htbp]
	\centering
	\caption{Lane detector work conditions}
	\label{lane_detector_condition}
	\begin{tabular}{ll}
		Frame rate                      &10fps \\
		Image format                    &8-bits RGB cv::Mat \\
		Image size                      &320x240 px	 \\	
		ROI (Region of Interest) size   &320x120 px
	\end{tabular}
\end{table}

@@

We executed tasks in user space, kernel space and irq task respectively, to evaluate real-time capability. We also compare performance among KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi \cite{WiringPi}, the most famous library for GPIO controlling on Raspberry Pi 3 (Broadcom bcm2709 SoC, 1.2GHz ARM Cortex-A53 CPU). The background system load was generated by Linux Test Project (LTP), which provides a collection of tools for validating the reliability, robustness, and stability of Linux. Unit of latency is microsecond in all measurement.

@@

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus. Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{placeins}

\usepackage{url}
\usepackage{listings}

@@

\begin{table}
	\centering
	\caption{Bill Of Materials}
	\label{hardware_list}
	\begin{tabular}{ll}
		Hardware                & Budgets  \\
		Raspberry Pi3 Model B   & 35.00 USD \\
		Raspberry Pi camera     & 23.15 USD  \\
		2S LiPo battery 1300mAh & 7.96 USD  \\
		Sandisk 16G microSD     & 6.13 USD  \\
		L298N motor driver      & 8.72 USD  \\
		Car frame               & 12.44 USD  \\
		DC voltage regulator    &  3.48 USD  \\
		Total                   & 96.88 USD
	\end{tabular}
\end{table}

@@

Our basic setup was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.

@@

The intrinsic matrix is also refering to the camera projection, and it is regarded as an ideal linear model consists of focal length, pixel size and principal point, the non-linear effects like lens distortion[\ref{fig:intrinsic}] are usually solved numerically.

@@

Figure \ref{fig:extrinsic} shows the result of Homography transformation, we exploit the transformation for the lane detection algorithm, the result is usually called the bird view image or inverse perspective mapping.

@@

@@

We executed tasks in user space, kernel space and irq task respectively, to evaluate real-time capability. We also compare performance among KsoftPWM, non-real-time PWM kernel module (nRTPKM) and WiringPi \cite{WiringPi}, the most famous library for GPIO controlling on Raspberry Pi 3 (Broadcom bcm2709 SoC, 1.2GHz ARM Cortex-A53 CPU). The background system load was generated by Linux Test Project (LTP) \cite{LTP}, which provides a collection of tools for validating the reliability, robustness, and stability of Linux. Unit of latency is microsecond in all measurement.

@@

Real-time performance is measured by stressing the system with LTP and applying cyclictest. \cite{cyclictest} We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus. Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai.

\subsection{Lane detector Performance}

The current state lane detector is implemented under OpenCV 2.4 and using single CPU core without GPU acceleration, further hardware optimization like: NEON, Intel TBB may help to speed up the overall performance.

\begin{table}[!htbp]
	\centering
	\caption{Lane detector performance and test conditions}
	\label{lane_detector_condition}
	\begin{tabular}{ll}
		Frame rate                      &10fps \\
		Image format                    &8-bits RGB cv::Mat \\
		Image size                      &320x240 px	 \\	
		ROI (Region of Interest) size   &320x120 px
	\end{tabular}
\end{table}
